SPARQL on the Open, Decentralised Web

### 2016-08-03 dissertation/introduction.tex
improve pseudograh desc

The use of IRIs makes it possible to view RDF statements as a directed
graph, where the subject IRI is a vertex, the predicate is an edge to
an object vertex\footnote{In general it is more precisely described as a
  partially labelled directed pseudograph with unique node labels}.

>>>>

The use of IRIs makes it possible to view RDF statements as a directed
graph, where the subject IRI is a vertex, the predicate is an edge to
an object vertex\footnote{A working draft of the RDF Semantics
  specification dated 23 January 2003, see
  \url{https://www.w3.org/TR/2003/WD-rdf-mt-20030123/}, described the
  graph structure as a partially labeled directed pseudograph with
  unique node labels.}.
